\section{Matched Baselines and Bridge-Validity Stress}

\paragraph{Matched baseline receipts.}
The schema-repaired report preserves every numerical field from its immutable
predecessor. Its deterministic audit replays 2,000
tables, 8,000 method rows, 12,000 diagnostics, and all aggregate cells with no
failure. This is a code-independent entry point and row-level recomputation,
but not independent human review. All digests are in the release manifest.

\begin{table}[t]
\centering
\small
\setlength{\tabcolsep}{3.0pt}
\begin{tabular}{lrrrr}
\hline
& \multicolumn{2}{c}{Hard boundary} & \multicolumn{2}{c}{Retention} \\
Rule & Deploy & False & Deploy & False \\
\hline
MOSAIC continuum & 0.0 & 0.0 & 57.9 & 0.0 \\
Holm LTT grid & 0.0 & 0.0 & 28.3 & 0.0 \\
Table-region grid & 0.0 & 0.0 & 0.0 & 0.0 \\
Deterministic adaptation & 0.0 & 0.0 & 0.0 & 0.0 \\
\hline
\end{tabular}
\caption{Complete matched-baseline outcomes (percent of 1,000 paired tables
per scenario). The LTT and table-region families contain the same 500 fixed
channel--decoder pairs.}
\label{supp:tab:matched-baselines}
\end{table}

MOSAIC's exact 95\% deployment interval is $[54.77,60.98]$ and Holm LTT's is
$[25.53,31.20]$. Their discordances are 312 MOSAIC-only and 16 LTT-only, with
267 joint deployments and 405 joint abstentions. The paired difference is
29.6 points. The exact two-sided McNemar value, computed only after the locked
audit, is $2.279\times10^{-72}$ and is descriptive. Zero false acceptances in
1,000 trials has exact 95\% upper endpoint 0.3682\% for each method--scenario
cell.

\paragraph{Bridge misspecification receipts.}
The audit replays 12,000 tables,
216,000 replicate fields, and 228 aggregate checks. It finds no failure of a
claimed bridge implication on the simultaneous confidence event.

\begin{table*}[t]
\centering
\small
\setlength{\tabcolsep}{5.2pt}
\begin{tabular}{lrrrrrr}
\hline
Target mechanism & Population min. $t$ & $n=500$ & $n=1000$ & $n=2000$ & $n=5000$ & Invalid false \\
\hline
Common source-blind transform & 1.000 & 0.0 & 31.0 & 100.0 & 100.0 & -- \\
Underdeclared contamination & .775 & 0.0 & 0.0 & 0.0 & 0.0 & 0/4,000 \\
Source-specific transforms & .500 & 0.0 & 0.0 & 0.0 & 0.0 & 0/4,000 \\
\hline
\end{tabular}
\caption{Bridge acceptance rates (percent of 1,000 tables per cell) for the
registered minimum retained mass $t\geq.80$. The two invalid mechanisms are
specific stress tests, not an exhaustive misspecification class.}
\label{supp:tab:bridge-misspecification}
\end{table*}

For the valid mechanism, the exact 95\% intervals are $[0,.368]$,
$[28.14,33.97]$, $[99.63,100]$, and $[99.63,100]$ percent as $n$ increases.
For every invalid cell, the exact 95\% upper endpoint is 0.3682\%. This power
transition is consistent with shrinking multinomial regions: evidence for a
valid common transform becomes decisive, while the registered violations stay
below the required retained mass.

\section{Real Data-Certified Bridge Study}

The 100-receipt manifest links the deterministic, exact-rational,
correction-scope, and comparator audits. Their digests are consolidated in the
release manifest.

\begin{table*}[t]
\centering
\small
\setlength{\tabcolsep}{4.6pt}
\begin{tabular}{lrrrrr}
\hline
Rule & $.30$ & $.35$ & $.40$ & $.45$ & $.49$ \\
\hline
Strict MOSAIC & 20/0 & 20/0 & 20/0 & 20/0 & 23/0 \\
Capacity transfer & 0/-- & 0/-- & 0/-- & 0/-- & 19/0 \\
Bridge plug-in & 38/6 & 47/7 & 47/7 & 62/18 & 77/16 \\
Validation plug-in & 68/15 & 76/15 & 80/18 & 92/26 & 100/18 \\
Always deploy validation & 100/47 & 100/39 & 100/38 & 100/34 & 100/18 \\
\hline
\end{tabular}
\caption{Deployments/observed diagnostic violations across 100 real jobs at
each worst-stratum error contract. Violation denominators include only
estimable deployments. Validation-only and unconditional rules deploy 20
unestimable Camelyon jobs at every threshold; strict MOSAIC abstains on them.}
\label{supp:tab:real-bridge-thresholds}
\end{table*}

At the primary $.40$ threshold, the bridge plug-in violation interval is
$[6.20,28.31]$ percent for 7/47, validation-only is $[18.85,43.21]$ for 18/60,
and unconditional deployment is $[36.21,58.98]$ for 38/80. Strict MOSAIC's
0/20 interval is $[0,16.84]$ percent, with one-sided 95\% upper bound 13.91\%.
Its 20 selections are six INLP, five LEACE, and nine MANCE++; at $.49$, three
Waterbirds jobs join the 20 BiasBios jobs. CivilComments and GaitPDB abstain
throughout, and all Camelyon jobs certify zero retained mass because a required
target source--label stratum is absent. This is the theorem's missing-support
case, whereas treating those 20 releases as safe would be statistically
unidentifiable.

\paragraph{Dataset grouping sensitivity.}
The 100 rows are 20 randomized jobs on each of five shared benchmarks, not 100
independent deployment domains. At the primary threshold, every one of the 20
strict deployments is on BiasBios-Clinical (median retained mass $.797$;
range $[.756,.858]$). Camelyon17 and GaitPDB have zero retained mass from
missing support; CivilComments and Waterbirds have no jointly feasible strict
source--utility release. A descriptive bootstrap that resamples the five
datasets gives a strict deployment-rate interval $[0,.60]$. Leaving out
BiasBios leaves zero strict deployments, whereas leaving out any other dataset
leaves 20. These summaries describe concentration of the experiment and do not
alter the per-job finite-sample guarantee.

\paragraph{Fresh corrected confirmation.}
Before any outcome from seeds 1220--1224, a separate lock fixed the same five
datasets, 13 official candidates, contracts, and new bridge--diagnostic splits.
Its strict-v2 manifest links the independent and exact-rational audits; their
digests appear in the consolidated checksum index. All 25 raw jobs have 13 rows and
zero optimization errors; strict replay reproduces 325 candidates and 350
global optimizations with no failure, and rational replay verifies every
serialized bridge and release. At $.40$, it deploys on 5/5 BiasBios jobs with
0/5 observed diagnostic violations (three INLP and two MANCE++), and abstains
on every one of the other 20 jobs. This is an untouched confirmation of the
corrected pipeline, while again showing that current real releases concentrate
on one benchmark.

The original v1 strict repair produced zero deployments at all five thresholds.
The locked scope audit finds 918 zero-to-positive retained-mass corrections,
all and only on label transforms with an identically zero output column. The
largest restoration is .857614. Every corrected original inequality has
nonnegative exact-rational slack. Thus v2 fixes a documented software
over-abstention bug; it does not weaken the certificate or erase the v1 record.
