\section{Notation and Exact Support Functions}

For one task label, let $P=(p_1,\ldots,p_G)$ collect the conditional fine-token
laws and let $M\in\mathrm{Stoch}(K,L)$ be a source-blind release channel. For an
attacker assignment $a\in[G]^L$, define
\begin{equation}
 v_{M,a,s}(c)=\sum_{z=1}^{L}M(c,z)\mathbf 1\{a(z)=s\}.
 \label{supp:eq:v}
\end{equation}
Every $v_{M,a,s}$ lies in $[0,1]^K$. The balanced Bayes accuracy has the two
equivalent forms
\begin{equation}
 \begin{aligned}
 A(P,M)&=\frac{1}{G}\sum_z\max_s(p_sM)(z)\\
 &=\frac{1}{G}\max_{a\in[G]^L}\sum_sp_s^\top v_{M,a,s}.
 \end{aligned}
 \label{supp:eq:bayes}
\end{equation}
The second identity follows because a finite-alphabet Bayes rule can be chosen
deterministically at each released token.

For empirical law $\widehat p$, radius $\epsilon$, and bounded score $v$, the
confidence-set support function is
\begin{equation}
 \Phi(\widehat p,\epsilon;v)=
 \max_{p\geq0,\,\mathbf 1^\top p=1,\,
 \|p-\widehat p\|_1\leq\epsilon}p^\top v.
 \label{supp:eq:support}
\end{equation}
Introducing positive and negative displacement variables gives a linear
program. Its compact dual is
\begin{align}
 \min_{\nu,\lambda,\theta}\quad
 &\nu+\widehat p^\top\theta+\epsilon\lambda,\\
 \text{s.t.}\quad
 &\nu+\theta_c\geq v_c\quad\forall c,\\
 &-\lambda\leq\theta_c\leq\lambda\quad\forall c,
 \qquad \lambda\geq0.
 \label{supp:eq:supportdual}
\end{align}
Strong duality holds because the primal confidence set is nonempty and compact.
The implementation also evaluates Eq.~\eqref{supp:eq:support} independently by
moving at most $\epsilon/2$ probability mass from low-score to high-score
coordinates, respecting simplex boundaries.

\section{Adaptive Confidence Envelope}

Let $\mathcal C_s=\{p\in\Delta_K:
\|p-\widehat p_s\|_1\leq\epsilon_s\}$ and define
\begin{equation}
 \overline A(\widehat P,M)=\frac{1}{G}
 \max_{a\in[G]^L}\sum_s
 \Phi(\widehat p_s,\epsilon_s;v_{M,a,s}).
 \label{supp:eq:abar}
\end{equation}

\begin{theorem}[Exact adaptive universal-attacker envelope]
On the event $\mathcal E=\{p_s\in\mathcal C_s\ \forall s,y\}$,
$A(P,M)\leq\overline A(\widehat P,M)$ simultaneously for every stochastic
release channel $M$, including one selected from the same table. For fixed
$M$, $\overline A$ is the exact supremum of $A(P,M)$ over
$\mathcal C_1\times\cdots\times\mathcal C_G$.
\end{theorem}

\begin{proof}
Using Eq.~\eqref{supp:eq:bayes}, take the supremum over the product confidence
set. The assignment family is finite, so the supremum and assignment maximum
commute. For a fixed assignment, the objective is additive in sources and the
confidence set is a Cartesian product, so each source maximization separates
and equals the support function in Eq.~\eqref{supp:eq:support}. This proves
exactness for every fixed $M$. On $\mathcal E$, the true law is one feasible
point in every confidence set, giving the upper bound. The statement is
pointwise over the complete channel space, so it remains true after any
measurable same-table selection of $M$.
\end{proof}

\begin{corollary}[Unconditional and label-aware attackers]
Let $X=(Y,C)$ and let $r_s$ denote the natural, unbalanced law
$P(X\mid S=s)$. Define the lifted channel
$\widetilde M((y,c),z)=M(c,z)$. Applying the theorem to
$(r_1,\ldots,r_G)$ certifies every source attacker observing $Z$ without
conditioning on $Y$. Replacing the output by $(Y,Z)$ and using
$\widetilde M((y,c),(y',z))=\mathbf1\{y=y'\}M(c,z)$ certifies the stronger
attacker that also observes the true label.
\end{corollary}

The corollary requires confidence regions for the natural joint laws and is
not implied by source--label-balanced sampling. The primary experiments instead
register the maximum label-conditional advantage, which removes the prevalence
channel by design.

For conditionally i.i.d. categorical observations within each stratum,
positive fixed count $n_{s,y}$, and an outcome-independent allocation
$\delta_{s,y}$, the confirmation uses
\begin{equation}
 \epsilon_{s,y}=\min\left\{2,
 \sqrt{\frac{2\log((2^K-2)/\delta_{s,y})}{n_{s,y}}}\right\}.
 \label{supp:eq:weissman}
\end{equation}
A union bound gives $\Pr(\mathcal E)\geq1-\sum_{s,y}\delta_{s,y}$. A zero-count
stratum receives radius two and is covered deterministically. The locked bridge
protocol used ``exchangeable'' informally for randomized held-out rows from the
same stratum; arbitrary exchangeability alone does not imply this concentration
bound, and is not claimed here.

\section{Data-Certified Shift Bridge}

For each source and task label, let
$\mathcal C_{s,y}$ be the reference confidence set above and let
\begin{equation}
 \mathcal D_{s,y}=\{q\in\Delta_K:
 \|q-\widehat q_{s,y}\|_1\leq\xi_{s,y}\}
 \label{supp:eq:bridge-set}
\end{equation}
be the confidence set from a labeled target bridge fold. Define
\begin{align}
 h_{s,y}(w)&=\max_{p\in\mathcal C_{s,y}}p^\top w,
 &\underline q_{s,y}(z)&=\min_{q\in\mathcal D_{s,y}}q(z).
 \label{supp:eq:bridge-support}
\end{align}
The coordinate lower bound is
$-\Phi(\widehat q_{s,y},\xi_{s,y};-e_z)$ and is therefore exact. For fixed
$y$, solve
\begin{equation}
 \begin{aligned}
 \widehat t_y=\max_{t,W}\quad&t\\
 \mathrm{s.t.}\quad&W_{cz}\geq0,\quad
 \sum_zW_{cz}=t &&\forall c,\\
 &h_{s,y}(W_{:z})\leq\underline q_{s,y}(z)
 &&\forall s,z,\\
 &0\leq t\leq1.
 \end{aligned}
 \label{supp:eq:bridge-lp}
\end{equation}
This is an LP. In particular, each support constraint is represented by
variables $(\nu_{s,z},\lambda_{s,z},\theta_{s,z})$ satisfying
\begin{align}
 \nu_{s,z}+\theta_{s,z,c}&\geq W_{cz} &&\forall c,\nonumber\\
 -\lambda_{s,z}\leq\theta_{s,z,c}&\leq\lambda_{s,z} &&\forall c,\nonumber\\
 \nu_{s,z}+\widehat p_{s,y}^{\top}\theta_{s,z}
 +\epsilon_{s,y}\lambda_{s,z}
 &\leq\underline q_{s,y}(z),\quad \lambda_{s,z}\geq0.
 \label{supp:eq:bridge-dual}
\end{align}
Strong duality for Eq.~\eqref{supp:eq:support} makes this epigraph exact.

\begin{theorem}[Adaptive finite-sample bridge membership]
Suppose the reference and bridge sets jointly cover all $p_{s,y}$ and
$q_{s,y}$. Any feasible $(t,W)$ in Eq.~\eqref{supp:eq:bridge-lp}, including its
same-table maximizer, satisfies, for $t>0$,
\begin{equation}
 q_{s,y}=t p_{s,y}T+(1-t)r_{s,y},\qquad T=W/t,
 \label{supp:eq:bridge-membership}
\end{equation}
for one source-blind stochastic $T$ and source-specific probability vectors
$r_{s,y}$.
\end{theorem}

\begin{proof}
Coverage and feasibility give, for every source and output coordinate,
\begin{equation}
 q_{s,y}(z)\geq\underline q_{s,y}(z)
 \geq h_{s,y}(W_{:z})\geq p_{s,y}^{\top}W_{:z}.
\end{equation}
Thus $d_{s,y}=q_{s,y}-p_{s,y}W$ is coordinatewise nonnegative. Since every row
of $W$ sums to $t$, $\mathbf1^\top d_{s,y}=1-t$. If $t<1$, set
$r_{s,y}=d_{s,y}/(1-t)$; if $t=1$, then $d_{s,y}=0$ and any residual law may be
used. Also, $T=W/t$ is row-stochastic. Every implication above holds
simultaneously for every feasible $(t,W)$ on one event, so choosing the
maximizer from the same confidence tables costs no additional multiplicity.
\end{proof}

\begin{proposition}[Robust optimality of the bridge LP]
Over the Cartesian product of all reference and bridge confidence sets,
Eq.~\eqref{supp:eq:bridge-lp} returns the largest retained mass for which one
fixed source-blind transform certifies Eq.~\eqref{supp:eq:bridge-membership}
uniformly over every law in that product.
\end{proposition}

\begin{proof}
For fixed $(t,T)$, the decomposition exists for a particular $(p,q)$ exactly
when $q_{s,y}-tp_{s,y}T$ is coordinatewise nonnegative: its coordinates then
sum to $1-t$ and can be normalized into a residual law. Requiring this for all
$(p,q)$ in the product region is equivalent to
\begin{equation}
 \max_{p\in\mathcal C_{s,y}}t(pT)(z)
 \leq\min_{q\in\mathcal D_{s,y}}q(z)\quad\forall s,z.
\end{equation}
The two extrema separate because the region is a Cartesian product.
Substituting $W=tT$ gives exactly the constraints of
Eq.~\eqref{supp:eq:bridge-lp}; Eq.~\eqref{supp:eq:bridge-dual} introduces no
relaxation. Maximizing $t$ proves the claim.
\end{proof}

\begin{corollary}[End-to-end target-population certificate]
Suppose $\widehat t_y>0$ for every required label. Insert the singleton
transform $\{\widehat T_y\}$ and contamination
$\widehat\eta_y=1-\widehat t_y$ from the bridge LP into the transform-exact
within-label source-distinguishability and utility optimizer. On the same joint event, every
same-table-selected release channel and decoder obeys its certified contracts
on the bridge population. This remains simultaneous across task labels,
registered utility thresholds, and finitely many released alphabet sizes when
their underlying reference and bridge tables share the registered allocation.
\end{corollary}

\begin{proof}
The bridge theorem establishes membership in the structured class used by the
transform-exact source-distinguishability and utility theorems below. Those theorems are
pointwise over every release channel and decoder on the same reference event.
Intersecting with the bridge confidence event and substituting the selected
singleton transform proves the result. Thresholds and alphabet sizes index
decisions made inside that already covered collection; separately learned
tokenizers or erasers still require familywise allocation across their
distinct tables.
\end{proof}

If a required bridge stratum has count zero, its honest set
$\mathcal D_{s,y}$ is the full simplex and every
$\underline q_{s,y}(z)=0$. For any $t>0$, the probability vector $p_{s,y}T$
has a positive coordinate, contradicting the corresponding bridge constraint.
Hence $\widehat t_y=0$. This is the operational missing-source boundary used in
the bridge confirmation.

\section{Channel Capacity and Common-Shift Transfer}

Define
\begin{equation}
 \operatorname{Cap}_G(M)=\frac{1}{G}
 \max_{a\in[G]^L}\sum_s\max_c v_{M,a,s}(c).
 \label{supp:eq:cap}
\end{equation}

\begin{lemma}[Exact arbitrary-shift capacity]
$\operatorname{Cap}_G(M)=\sup_{r_1,\ldots,r_G\in\Delta_K}A(R,M)$.
\end{lemma}

\begin{proof}
Expand $A(R,M)$ by Eq.~\eqref{supp:eq:bayes}. For fixed assignment $a$, each
source law $r_s$ can concentrate all mass on a token maximizing
$v_{M,a,s}(c)$. The source suprema separate and the finite maxima commute,
yielding Eq.~\eqref{supp:eq:cap}.
\end{proof}

For two sources, uniform-prior Bayes accuracy is
$(1+\operatorname{TV}(r_1M,r_2M))/2$. The diameter of the convex hull of channel
rows is attained by two rows, hence
$2\operatorname{Cap}_2(M)-1=max_{c,c'}
\operatorname{TV}(M(c,\cdot),M(c',\cdot))$, the Dobrushin coefficient.

For common pre-release channel $T$, define
\begin{equation}
 \rho_T(M)=\max_c\operatorname{TV}((TM)(c,\cdot),M(c,\cdot)).
 \label{supp:eq:rho}
\end{equation}

\begin{lemma}[Approximate invariance transfer]
For every source experiment $P$,
\begin{equation}
 A(P,TM)\leq
 \min\{\operatorname{Cap}_G(M),A(P,M)+\rho_T(M)\}.
 \label{supp:eq:transfer}
\end{equation}
\end{lemma}

\begin{proof}
For source $s$, convexity of total variation gives
$\operatorname{TV}(p_sTM,p_sM)\leq
\sum_cp_s(c)\operatorname{TV}((TM)(c,\cdot),M(c,\cdot))\leq\rho_T(M)$.
The success probability of any attacker changes by at most this distance.
Averaging over sources and maximizing the attacker gives the additive bound.
The capacity bound follows by treating $p_sT$ as an arbitrary fine-token law
and applying the preceding lemma.
\end{proof}

\section{Structured External Shift}

For label $y$, suppose
\begin{equation}
 q_s=t_yp_sT_y+(1-t_y)r_s,
 \qquad t_y\geq1-\eta_y,
 \label{supp:eq:model}
\end{equation}
with common $T_y\in\mathcal T_y$ and common retained mass $t_y$ across sources.
For a polytope with finite extremes
$\mathcal V_y=\operatorname{ext}(\mathcal T_y)$, define
\begin{equation}
 \begin{aligned}
 \overline A_y^X(M)
 &=\frac1G\max_{T\in\mathcal V_y,\,a\in[G]^L}\sum_s\Big[
 \\[-2pt]&\quad (1-\eta_y)
 \Phi(\widehat p_{s,y},\epsilon_{s,y};Tv_{M,a,s})
 \\[-2pt]&\quad +\eta_y\max_cv_{M,a,s}(c)\Big].
 \end{aligned}
 \label{supp:eq:exactconfidence}
\end{equation}

\begin{theorem}[Transform-exact post-selection certificate]
On $\mathcal E$, simultaneously for every selected $M$ and every external law
in Eq.~\eqref{supp:eq:model}, $A(Q,M)\leq\overline A_y^X(M)$. For fixed $M$,
the right-hand side is the exact supremum over the product confidence sets,
transform polytope, allowed retained masses, and residual laws.
\end{theorem}

\begin{proof}
Expand balanced Bayes accuracy using Eq.~\eqref{supp:eq:bayes}. For fixed
$T,t$, and attacker assignment, the source confidence sets and residual
simplexes separate. Their support values are
$\Phi(\widehat p_{s,y},\epsilon_{s,y};Tv_{M,a,s})$ and
$\max_cv_{M,a,s}(c)$. The latter is no smaller because every coordinate of
$Tv$ is a convex combination of coordinates of $v$. The maximizing retained
mass is therefore $t=1-\eta_y$. The resulting confidence support is convex in
$T$, so its maximum over a polytope is attained at an extreme. All remaining
maxima are finite and commute. This gives exactness for fixed $M$; pointwise
coverage over all channels preserves the bound after same-table selection.
\end{proof}

For a transform family that cannot be enumerated, let
$B_y(M)=\min\{\operatorname{Cap}_G(M),
\overline A_y(\widehat P,M)+\rho_{\mathcal T_y}(M)\}$.

\begin{corollary}[Capacity-transfer fallback]
On $\mathcal E$,
\begin{equation}
 A(Q,M)\leq(1-\eta_y)B_y(M)
 +\eta_y\operatorname{Cap}_G(M).
 \label{supp:eq:shiftbound}
\end{equation}
\end{corollary}

\begin{proof}
The retained experiment is bounded by Eq.~\eqref{supp:eq:transfer}, the
adaptive envelope bounds its unknown reference term, and residuals are bounded
by capacity. Since $B_y(M)\leq\operatorname{Cap}_G(M)$, the largest value over
$t_y\geq1-\eta_y$ occurs at $t_y=1-\eta_y$.
\end{proof}

The exact confidence envelope is no larger than this fallback because it is
the supremum over the same set. At zero confidence radius, it becomes the
known-population external risk
\begin{equation}
 \begin{aligned}
 \frac{1}{G}\max_{T\in\operatorname{ext}(\mathcal T_y),\,a\in[G]^L}
 \sum_s\big[&(1-\eta_y)p_{s,y}^\top T v_{M,a,s}\\
 &+\eta_y\max_cv_{M,a,s}(c)\big].
 \end{aligned}
 \label{supp:eq:exactprivacy}
\end{equation}
used by the separately implemented synthetic evaluator.

\section{Utility Certificate}

Fix decoder $g:[L]\to[J]$, let
$\ell_y(z)=\mathbf 1\{g(z)\neq y\}$, and write
$u_y=M\ell_y$. Define
\begin{align}
 \overline E_{s,y}(M,g)&=
 \Phi(\widehat p_{s,y},\epsilon_{s,y};u_y),\\
 \kappa_y(M,g)&=\sup_{T\in\mathcal T_y}
 \max\{0,\max_c((TM-M)\ell_y)(c)\},\\
 U_y(M,g)&=\max_cu_y(c).
\end{align}

Define the transform-exact value
\begin{equation}
 \begin{aligned}
 \overline E^X_{s,y}(M,g)
 &=\max_{T\in\mathcal V_y}\Big[(1-\eta_y)
 \\[-2pt]&\quad\Phi(\widehat p_{s,y},\epsilon_{s,y};Tu_y)
 +\eta_y\max_cu_y(c)\Big].
 \end{aligned}
 \label{supp:eq:exactutilityconfidence}
\end{equation}

\begin{corollary}[Transform-exact adaptive utility certificate]
On $\mathcal E$, every selected $(M,g)$ satisfies
$\operatorname{Err}_{s,y}(Q,M,g)\leq\overline E^X_{s,y}(M,g)$, and the
right-hand side is exact over the stated confidence ball and shift class.
\end{corollary}

\begin{proof}
Repeat the transform-exact proof for bounded loss $\ell_y$, without averaging
over sources or maximizing an attacker assignment.
\end{proof}

The capacity fallback is
\begin{corollary}[Adaptive shifted-utility fallback]
On $\mathcal E$, every selected $(M,g)$ satisfies
\begin{equation}
 \operatorname{Err}_{s,y}(Q,M,g)\leq
 (1-\eta_y)D_{s,y}(M,g)+\eta_yU_y(M,g),
 \label{supp:eq:utility}
\end{equation}
where
$D_{s,y}=\min\{U_y,\overline E_{s,y}+\kappa_y\}$.
\end{corollary}

\begin{proof}
Apply the structured-shift proof to the bounded loss $\ell_y$. The common
component differs from its reference expectation by at most the largest
positive directional defect $\kappa_y$, while the arbitrary residual
concentrates on a row with maximal error $U_y$.
\end{proof}

The transform-exact utility value is never larger than this fallback.

The exact population utility risk used in the independent evaluator is
\begin{equation}
 \max_{T\in\operatorname{ext}(\mathcal T_y)}
 \left[(1-\eta_y)p_{s,y}^\top TM\ell_y
 +\eta_y\max_c(M\ell_y)(c)\right].
 \label{supp:eq:exactutility}
\end{equation}

\section{No-Free-Lunch Boundary}

\begin{theorem}[Unrestricted differential shift]
For $G\geq2$, $\operatorname{Cap}_G(M)=1/G$ if and only if all rows of $M$ are
identical.
\end{theorem}

\begin{proof}
Identical rows make every released source law identical. Conversely, if two
rows differ, choose two residual source laws concentrated on those rows and
place every remaining source on either row. The released source laws are not
all identical, so uniform-prior Bayes accuracy is strictly above chance.
Exactness of Eq.~\eqref{supp:eq:cap} completes the argument.
\end{proof}

For two fine tokens $c_0,c_1$ with different task labels, suppose a decoder has
row-wise errors at most $e_0,e_1$. The decoder decision event occurs with
probability at least $1-e_0$ under $M(c_0,\cdot)$ and at most $e_1$ under
$M(c_1,\cdot)$. Total variation is therefore at least $1-e_0-e_1$, giving
\begin{equation}
 2\operatorname{Cap}_2(M)-1\geq1-e_0-e_1.
 \label{supp:eq:utilitylower}
\end{equation}
Thus a nontrivial task contract is incompatible with chance-level source
capacity under unrestricted differential shift.

\section{Repeated Queries and Side Information}

\begin{proposition}[Persistent-query equivalence]
Suppose the runtime samples one token $Z$ per immutable item and every later
query returns that stored token. For any finite or countably infinite number of
queries, the complete transcript has exactly the same source-inference Bayes
accuracy as one observation of $Z$.
\end{proposition}

\begin{proof}
Every persistent transcript has the form $(Z,Z,\ldots)$. The transcript is a
deterministic function of $Z$, while $Z$ is recovered from its first
coordinate. They therefore generate the same sigma-field. The classes of
measurable source decisions based on either observation coincide, so their
optimal balanced accuracies are equal.
\end{proof}

Fresh independent draws are a different mechanism. For a registered budget
$r$, define the product channel
\begin{equation}
 M^{\otimes r}(c,z_{1:r})=\prod_{j=1}^{r}M(c,z_j).
 \label{supp:eq:product-channel}
\end{equation}

\begin{proposition}[Exact bounded-query reduction]
An attacker observing $r$ conditionally independent fresh releases sees
exactly one output of $M^{\otimes r}$. Substituting this product channel into
the adaptive, bridge, structured-shift, and capacity results gives an exact
certificate for that query budget, without a union bound over queries.
\end{proposition}

\begin{proof}
Conditioned on fine token $c$, the transcript probability mass function is the
right-hand side of Eq.~\eqref{supp:eq:product-channel}. Every theorem depends
on the release mechanism only through this conditional channel. Replacing the
output alphabet $[L]$ by $[L]^r$ therefore reproduces the transcript experiment
exactly. The alphabet has size $L^r$, which is a computational rather than a
statistical restriction.
\end{proof}

\begin{proposition}[Unbounded fresh-query failure]
If two rows $M(c,\cdot)$ and $M(c',\cdot)$ differ, then their $r$-fold product
laws have total variation tending to one. Consequently the binary
source-inference capacity of $M^{\otimes r}$ tends to one as $r\to\infty$.
\end{proposition}

\begin{proof}
For distinct finite-alphabet laws $u$ and $v$, their Hellinger affinity
$\alpha=\sum_z\sqrt{u(z)v(z)}$ is strictly below one. Product affinity equals
$\alpha^r$, and
$\operatorname{TV}(u^{\otimes r},v^{\otimes r})\geq1-\alpha^r\to1$.
Concentrating two source laws on fine tokens $c$ and $c'$ makes binary balanced
Bayes accuracy
$(1+\operatorname{TV})/2\to1$. The capacity is at least this value and at most
one.
\end{proof}

The registered attacker observes the persistent token, knows the complete
mechanism, and has no additional item-level side information. If a variable
$H$ is also public, the relevant experiment is $(Z,H)$, not $Z$; it must be
included in the fine/output alphabet and certified jointly. In particular,
original features, source-dependent metadata, mutable identifier behavior,
timing, and private mechanism state are outside the theorem. A production
runtime must durably bind each versioned item identifier to one immutable fine
token and one sampled output; rebinding or silent rerandomization violates the
registered mechanism.

Persistence is an item-level statement, not a population-level composition
theorem. Tokens from distinct items associated with one source form a joint
experiment. Even when each item is persistent, independent observations from
different items can increase source distinguishability, while correlations,
adaptive mechanisms, stopping times, and observable query counts can change the
joint law further. Such access requires a certificate for the complete
multi-item transcript. The product-channel proposition applies only to repeated
conditionally independent draws from one fixed fine token under one fixed
channel and a noninformative registered query count.

\section{Missing-Source Non-Identifiability}

Fix two required sources and a released-token law $q_0M$ for source zero.
Suppose an external audit contains no source-one rows, so its observed-data
distribution is identical for every $q_1\in\Delta_K$. Define
\begin{equation}
 A_{\rm miss}(q_0,M)=\sup_{q_1\in\Delta_K}A((q_0,q_1),M).
 \label{supp:eq:missing}
\end{equation}

\begin{theorem}[Missing-source non-identifiability]
Fix $q_0$, $M$, and $\tau$ independently of the missing-source law and the
audit randomness. Let a possibly randomized protocol observe no source-one rows and claim
$A((q_0,q_1),M)\leq\tau$. If its false-certification probability is at most
$\delta<1$ uniformly over every $q_1$, then for
$\tau<A_{\rm miss}(q_0,M)$ it can issue that claim with probability at most
$\delta$.
\end{theorem}

\begin{proof}
The finite-simplex supremum is attained; call a maximizer $q_1^*$. The audit's
observed-data distribution does not depend on the missing law. Consequently,
every event on which the protocol claims a bound below
$A((q_0,q_1^*),M)$ is a false-certification event under $q_1^*$, and uniform
validity limits that event to probability $\delta$.
\end{proof}

The same indistinguishability argument for a missing source--label utility
stratum replaces Eq.~\eqref{supp:eq:missing} by
$\max_c(M\ell_y)(c)$. These are precisely the full-simplex terms used when a
stratum has count zero. Moreover, if $M$ is nonconstant, then
$A_{\rm miss}(q_0,M)>1/2$ for every $q_0$: the mixture $q_0M$ cannot equal every
nonidentical channel row, and a missing source concentrated on a differing row
has positive total-variation distinguishability. Missing required strata must
therefore be reported as unestimable unless an external structural assumption
identifies their laws.

\section{Abstention Theory}

Let $V(P,e)$ be the globally optimal certified worst conditional error for
confidence balls centered at $P$ with common radius $e$. With deployed radius
$e_n$, define
$r_n^*=\sup\{r\geq0:V(P,e_n+r)\leq\tau_U\}$.

\begin{proposition}[Finite-sample abstention envelope]
For $H$ registered strata of size $n$,
\begin{equation}
 \Pr(\text{MOSAIC abstains})\leq
 \min\{1,H(2^K-2)e^{-n(r_n^*)^2/2}\}.
 \label{supp:eq:abstain}
\end{equation}
\end{proposition}

\begin{proof}
If every empirical stratum is within distance $r$ of its population law, each
radius-$e_n$ ball around the empirical law is contained in the
radius-$(e_n+r)$ ball around the population law. A feasible population-centered
pair for the larger balls remains feasible for the empirical problem. Apply
the Weissman bound and a stratum union bound, then let $r$ approach $r_n^*$.
\end{proof}

For the preregistered local power curve, write $V_n(P)=V(P,e_n)$. Under local
uniqueness of the decoder and certificate branches together with strong
regularity of the resulting parametric linear program, the value is
differentiable. If $h_{n,s,y}$ is its simplex gradient and
$\Sigma_{s,y}=\operatorname{diag}(p_{s,y})-p_{s,y}p_{s,y}^\top$, the finite-$n$
delta-method prediction is
\begin{equation}
 \Phi_{\mathrm N}\!\left(
 \frac{\tau_U-V_n(P)}{
 \sqrt{n^{-1}\sum_{s,y}h_{n,s,y}^\top\Sigma_{s,y}h_{n,s,y}}}
 \right).
 \label{supp:eq:power}
\end{equation}
The locked analysis estimates each gradient by centered simplex-preserving
finite differences at step sizes $10^{-4}$ and $5\times10^{-5}$ and rejects the
approximation if their maximum discrepancy exceeds $5\times10^{-3}$.

\section{Optimization Certificate}

For completeness, fix a decoder $g$ and write
$b_{y,T,a,s}$ for the support-function epigraph with score
$Tv_{M,a,s}$, $c_{a,s}\geq v_{M,a,s}(c)$ for every $c$, and
$d_{s,y,T}$ for the utility support epigraph with score $TM\ell_y$. Each $b$
and $d$ is represented by the dual in Eq.~\eqref{supp:eq:supportdual}; its score
is linear in $M$. The transform-exact LP is
\begin{align}
 \min_{M,\zeta}\quad&\zeta
 \label{supp:eq:exact-lp}\\
 \mathrm{s.t.}\quad&M_{cz}\geq0,\quad\sum_zM_{cz}=1 &&\forall c,\nonumber\\
 &\frac1G\sum_s\left[(1-\eta_y)b_{y,T,a,s}
 +\eta_yc_{a,s}\right]\leq\tau^{\rm BA}_{P,y}
 &&\forall y,T,a,\nonumber\\
 &(1-\eta_y)d_{s,y,T}+\eta_yu_y^{\max}\leq\zeta
 &&\forall s,y,T,\nonumber
\end{align}
where $u_y^{\max}\geq(M\ell_y)(c)$ for every $c$ and
$\tau^{\rm BA}_{P,y}=G^{-1}+(1-G^{-1})\tau_{P,y}$. All epigraph variables are
minimized indirectly or upper-constrained, so an optimum can take each at its
smallest valid value. Enforcing every finite transform extreme and all $G^L$
attacker assignments exactly implements the maxima in the certificates.
Enumerating all $J^L$ decoders and taking the smallest objective returns the
global transform-exact finite-alphabet solution.

For the capacity fallback, each expression
$\min\{\operatorname{Cap}_G(M),\overline A_y+\rho_y\}$ and
$\min\{U_y,\overline E_{s,y}+\kappa_y\}$ is represented by a binary disjunction.
With branch bit $b$, the first branch constraint is relaxed by $2b$ and the
second by $2(1-b)$; all constituent quantities lie in ranges for which two is a
valid big-$M$ constant. The implementation analogously disjoins the utility
branches, then enumerates decoders. Thus the fallback is a finite MILP, not a
local nonlinear search.

Globality is asserted only when every decoder and attacker assignment is
enumerated, the exact LP reports an optimal status or the fallback MIP gap is
at most $10^{-10}$, and the solver feasibility tolerance is $10^{-9}$.
The original bridge run preserves raw solver outputs, but claim-grade decisions
come from a strict replay triggered by an adversarial proof audit. It contracts
retained mass using a $10^{-9}$ outward guard until every independently
recomputed membership slack is nonnegative, optimizes source constraints with
a $10^{-6}$ inward margin, adds $10^{-9}$ to recomputed risk bounds, and
compares those outward values with the original thresholds using zero decision
tolerance. A timeout, negative membership slack, oversized assignment family,
or post-solve mismatch can only abstain. The disclosed v2 correction to this
repair is detailed below.

The exact audit checks zero-radius agreement with a separate population
evaluator, binary confidence-ball endpoints, 100 randomized dominance
comparisons with the fallback, and dense channel grids. The fallback audit
compares 30 randomized small instances with exhaustive $21^K$ grids and
includes a witness in which the best stochastic certified error is $0.371588$
while every deterministic release has certified error $1$.

\section{Locked Experimental Protocol}

The synthetic population has two labels, two sources, and three fine tokens.
For label zero the source laws are $(0.80,0.15,0.05)$ and
$(0.65,0.30,0.05)$; for label one they are $(0.05,0.20,0.75)$ and
$(0.05,0.35,0.60)$. The common-transform set is the convex hull of identity and
a nearest-neighbor smoothing channel. The hard safety scenario uses
$\eta=0.20$, source-advantage threshold $0.30$, and worst conditional error
threshold $0.40$. The retention scenario uses $\eta=0.10$, thresholds $0.35$
and $0.45$. Every source--label stratum contains exactly $n$ independent draws.

The confirmation fixes 1,000 replicates in each of three hard-scenario and five
retention-scenario sample-size cells. It compares eight rules and stores 64,000
method-level receipts. The preregistration fixes all seeds, methods, intervals,
and pass criteria, hashes the theorem and implementation, and was pushed before
the confirmation began. Pilot seeds zero through 199 are excluded. The oldest
aggregate-only pilot is retained as design history but cannot support a
channel-level claim; every later pilot row is replayed by the exact evaluator.

\paragraph{Matched finite-family baselines.}
A separately locked extension evaluates the same 1,000 paired tables per
scenario with a $5^3$ grid of binary-output stochastic channels and all $2^2$
binary decoders, for 500 channel--decoder pairs. The confidence-region grid
applies MOSAIC's one simultaneous pre-channel event but restricts optimization
to these 500 pairs. The deterministic baseline applies the same shift-aware
certificate to every deterministic three-to-two map. We report it as a
deterministic restricted-encoder baseline, not as FARE: official FARE trains a
fair decision tree for demographic parity on a different raw-input protocol,
whereas the present study evaluates within-label source inference under a
pre-release geographic-shift contract. An end-to-end FARE number would not be
commensurate with this contract.

The LTT baseline tests every fixed pair without reusing MOSAIC's table region.
Index its source-attacker and source--label utility inequalities by $j$. After
removing the known contamination term, each has an empirical mean
$\widehat\mu_j$, unsafe null $H_j:\mu_j\geq b_j$, and effective sample size
$n_j$ (or $Gn$ for a balanced attacker average over $G$ source strata). Its
one-sided Hoeffding value is
\begin{equation}
 p_j=\exp\{-2n_j(b_j-\widehat\mu_j)_+^2\}.
 \label{supp:eq:lttcomponent}
\end{equation}
The unsafe candidate null is the union of its component nulls, so
$p_{\rm cand}=\max_j p_j$ is valid by an intersection--union test: whenever any
$H_j$ holds, rejection at level $\alpha$ implies rejection of that true
component at level $\alpha$. Holm step-down then controls familywise false
certification across all 500 candidates at $\delta=.05$. Among rejected
candidates, LTT selects the smallest point-estimated worst error with a fixed
index tie break; no rejection means abstention. The population evaluator grades
all four rules on the paired untouched law, including every abstention and
false acceptance.

The data-certified bridge confirmation was locked separately after excluding
all real-study seeds through 1199. It runs seeds 1200--1219 on Waterbirds,
Camelyon17-WILDS, CivilComments-WILDS, BiasBios-Clinical, and GaitPDB. Within
each represented target source--label stratum, a deterministic seeded split
assigns two thirds to the bridge and one third to an untouched diagnostic set.
The frontier has identity plus twelve settings from pinned official INLP,
LEACE, R-LACE, TaCo, and MANCE++ repositories, with no proxy implementations.
Each of 13 candidates has one reference and one bridge table; familywise
$\delta=0.05$ is divided across these 26 tables, and each table's allocation is
divided across its four source--label strata. Thus each multinomial radius uses
$\delta/(13\cdot2\cdot4)$. The same event covers all bridge transforms,
two- and four-token release optimizers, and utility thresholds
$\{0.30,0.35,0.40,0.45,0.49\}$.

The primary rule uses $L=2$, maximum source advantage $0.35$, and maximum
worst-stratum error $0.40$. It selects the feasible candidate with minimum
bridge-certified error and a lexical tie break. The minimum-error candidate is
then reoptimized at $L=4$ without inspecting diagnostics. All 100 dataset--seed
jobs, 1,300 candidate rows, and 1,400 global optima are required; the stopping
rule forbids outcome-based replacement or omission. Confirmatory gates require
zero optimization errors, zero primary diagnostic contract violations, at
least 16 estimable primary deployments, BiasBios deployment on at least 16/20
seeds at threshold $0.40$ and 14/20 at $0.35$, pointwise noninferiority of the
globally optimized $L=4$ objective, and zero retained mass for every Camelyon
job with missing bridge support. The claim is restricted to populations drawn
i.i.d. from the same target stratum laws as the bridge fold and is not a
clinical-safety claim.

After 27 of 100 raw receipts had been written, but before any receipt contents
or outcomes were inspected, an adversarial proof audit identified that the
original tolerance-based acceptance rule did not justify an exact software
contract. A hash-locked numerical amendment therefore supersedes every raw
bridge decision with the strict replay above. The amendment records the timing,
the information seen (filenames, counts, timestamps, and process status only),
all code hashes, the zero-tolerance decision rule, and the requirement to replay
all 1,400 optima regardless of outcome. Both raw and strict receipts remain
public so this correction cannot be hidden.

After the complete v1 strict audit, we found that its repair added the guard to
the denominator of every output constraint, including a transform column that
was identically zero. The exact constraint for such a column is
$\underline q_{s,y}(z)\geq t_y\cdot0$ and cannot restrict $t_y$; replacing the
zero by $10^{-9}$ incorrectly collapsed retained mass to zero. All v1 outcomes
had already been inspected and showed zero deployments. Before any corrected
replay, a second hash lock disclosed that timing and froze a single change:
omit the guard-ratio contraction only when every entry of the complete
transform output column is exactly zero, then recheck every original slack,
including that column. No table, candidate, threshold, radius, split, release
optimizer, or diagnostic changed. The scope audit compares all 2,600 label
certificates: all 918 changed labels have the required structural zero and no
other label changes. Deterministic replay matches all 100 v2 receipts; exact
rational arithmetic verifies nonnegative slack for all 1,300 bridges and
outward bounds for all 1,400 releases. The v1 receipts remain part of the
artifact and v2 is identified as post-audit corrective evidence.

\input{mosaic_supplement_results}

\input{mosaic_bridge_supplement_results}

\input{mosaic_transform_exact_supplement_results}

\input{mosaic_real_current_evidence}

\input{mosaic_acs_natural_shift_supplement_results}

\input{mosaic_path9_supplement_results}

\section{Registered Qwen Pilot Boundary}

A prewritten unlocked pilot evaluated six Qwen2.5-1.5B-Instruct hidden-state
interfaces on 12,264 CivilComments-WILDS examples. Integer dataset IDs divisible
by four formed the pilot population; every later confirmation ID was excluded.
The familywise $.05$ budget covered three fixed pooling rules, $K\in\{4,8\}$,
and both reference and bridge tables. The go rule required complete strata,
minimum retained mass at least $.50$, a nonconstant release, source advantage
at most $.35$, and certified worst error at most $.49$.

No candidate passed. The layer-14 and final-layer mean-pooled $K=4$ channels
were nonconstant, with retained masses $.6154$ and $.6557$, but their certified
worst errors were $.492292$ and $.490117$. Every $K=8$ candidate and the
final-token $K=4$ candidate returned a constant release with error $.5$. An
independent audit verifies all six candidates, all role--label--source counts,
zero confirmation-ID overlap, every manifest hash, and the exact stopping rule.
Consequently no temporal confirmation was registered and the main paper makes
no LLM-interface claim.

\section{Reproducibility Manifest}

MOSAIC optimization, confirmations, and audits ran on an Apple M4 system with
10 CPU cores and 16 GB unified memory under macOS 26.2 (arm64). The locked
Python environment was Python 3.12.13 with NumPy 2.5.1, SciPy 1.18.0,
scikit-learn 1.9.0, PyTorch 2.13.0, and the HiGHS LP/MILP backend exposed by
SciPy. No GPU is
required once the registered feature stores have been constructed; synthetic
confirmation and every replay are CPU-only.

The named package reports the exact preregistration hash, Git commit, software
versions, and artifact hashes. The anonymous package retains the same internal
identifiers while replacing public authorship and repository metadata as
required by double-blind review. Raw synthetic receipts contain no private or
human-subject data. Real-domain experiments, if included, retain dataset terms,
official split definitions, preprocessing hashes, and method-specific code
provenance in a separate manifest.

The repository is also installable as \texttt{mosaic-certified-release}. Its
public path is \texttt{fit}, \texttt{certify}, then
\texttt{release\_or\_abstain}; the runtime persists one sampled token per item
after certification and fails closed after missing support or invalid
recertification. The anonymous archive contains the same package with sanitized
authorship metadata and focused end-to-end tests.

\begin{table}[t]
\centering
\scriptsize
\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{p{.54\columnwidth}p{.36\columnwidth}}
\hline
Artifact group & Checksum index \\
\hline
Main and supplement PDFs & V12 release SHA-256 manifest \\
Locked protocols and reports & Anonymous code/data manifest \\
Real compact receipts and audits & Anonymous code/data manifest \\
Post-review stress, scaling, natural shift, and Qwen pilot & V12 release SHA-256 manifest \\
\hline
\end{tabular}
\caption{Single-entry checksum map. Full digests are stored once in the two
machine-readable release manifests rather than repeated in prose.}
\label{supp:tab:checksum-map}
\end{table}
