\section{Official-Method Feature Results}

All 25 dataset--seed jobs and all 325 registered candidate pairs completed with
no proxy implementations or optimization failures. All ten preregistered gates
pass. The independent replay reconstructed every confidence radius,
certificate, selected channel, decoder, external diagnostic, lexical tie break,
and 650 global optima with zero mismatch. Table \ref{tab:realfrontier} reports
the complete selection behavior.

\begin{table*}[t]
\centering
\footnotesize
\setlength{\tabcolsep}{3.2pt}
\begin{tabular}{llclcl}
\hline
Dataset & Modality & Deploy F$\to$X & Exact family & Exact error & External diagnostic \\
\hline
Waterbirds & vision & $0/5\!\to\!1/5$ & INLP (1) & .490 & 5/65 rows safe; selected row safe \\
Camelyon17-WILDS & medical vision & $5/5\!\to\!5/5$ & INLP (2), LEACE (3) & .248 & unestimable: source absent \\
CivilComments-WILDS & text & $0/5\!\to\!0/5$ & -- & .500 & 0/65 candidate rows safe \\
BiasBios-Clinical & clinical text & $5/5\!\to\!5/5$ & INLP (3), R-LACE (2) & .291 & 5/5 selected; 65/65 rows safe \\
GaitPDB & time series & $0/5\!\to\!0/5$ & -- & .500 & 0/65 candidate rows safe \\
\hline
\end{tabular}
\caption{Fresh locked paired frontier, five seeds per dataset and 13 candidates
per seed. F and X denote fallback and transform-exact certificates. ``Best
exact error'' is the mean minimum exact value across the five jobs. External
diagnostics are descriptive and do not establish structured-shift membership.}
\label{tab:realfrontier}
\end{table*}

The paired comparison isolates the refinement. The exact objective is no larger
on all 325 rows and is strictly smaller on 135, with mean and maximum reductions
of 1.04 and 3.45 percentage points. Candidate deployments increase from 130 to
131. On Waterbirds seed 107, exact INLP rank 4 crosses the contract at certified
error .465; its external error is .291 and source advantage is .057. This is the
one additional selected deployment registered by the protocol, and it is safe
on the natural diagnostic.

BiasBios supplies the repeated positive case. Every official candidate clears
both exact contracts on all five seeds; MOSAIC selects INLP three times and
R-LACE twice. The selected mean certified worst error is .291 (range
.281--.297), while the natural diagnostic has mean worst error .207 and mean
source advantage .047. All five selections are externally safe.

CivilComments and GaitPDB remain utility-limited: within-label source distinguishability is controlled only with
certified error .50, so all ten jobs abstain. Four Waterbirds jobs also abstain.
Camelyon17 yields five model-conditional releases, but every natural external
split lacks a required source class; the missing-source theorem forces those
diagnostics to remain unestimable. Across the six externally estimable exact
selections there are zero false acceptances. This is a low-powered diagnostic
(95\% exact upper bound 45.9\%), not evidence that the benchmark populations
belong to Eq.~\eqref{eq:shift}.
