\section{Official-Method Real-Feature Receipts}

\paragraph{Fresh paired confirmation.}
The untouched seeds are 105--109; pilots 0--4 and the earlier real-feature
seeds 100--104 are excluded. The protocol was locked before these outcomes with
SHA-256 digest
\texttt{d88d42e813d65c7d725e923c94be0518}\allowbreak
\texttt{d7049e0b62131be96ffbec748d5e5775}. All 25 jobs and 325 candidate pairs
complete with official INLP, LEACE, R-LACE, TaCo, and MANCE++ implementations
and no proxy or failed row. All ten registered gates pass.

The frontier order is identity; INLP ranks 1, 2, 4, and 8; LEACE; R-LACE ranks
1 and 4; TaCo with 1, 2, 3, and 5 removed components; and MANCE++. Every
candidate stores its pinned repository, commit, entry point, and parameters.
Each separately fitted tokenizer receives $\delta/13$; both certificate
variants optimize a continuum of channels from the same covered table.

\begin{table}[t]
\centering
\small
\setlength{\tabcolsep}{2.6pt}
\begin{tabular}{rlrrr}
\hline
Dataset/seed & Exact selection & Cert. & Ext. error & Ext. adv. \\
\hline
BiasBios 105 & R-LACE rank 1 & .2969 & .1902 & .0579 \\
BiasBios 106 & INLP rank 4 & .2882 & .2143 & .0380 \\
BiasBios 107 & INLP rank 4 & .2920 & .2011 & .0711 \\
BiasBios 108 & R-LACE rank 4 & .2952 & .2390 & .0610 \\
BiasBios 109 & INLP rank 4 & .2814 & .1881 & .0082 \\
Waterbirds 107 & INLP rank 4 & .4651 & .2905 & .0569 \\
\hline
\end{tabular}
\caption{Every externally estimable transform-exact selection. All six pass
the natural external diagnostic.}
\label{supp:tab:exact-estimable-selections}
\end{table}

\begin{table}[t]
\centering
\small
\setlength{\tabcolsep}{4.0pt}
\begin{tabular}{rllr}
\hline
Seed & Fallback selection & Exact selection & Exact cert. \\
\hline
105 & LEACE & INLP rank 1 & .2598 \\
106 & LEACE & LEACE & .2302 \\
107 & LEACE & LEACE & .2492 \\
108 & LEACE & LEACE & .2590 \\
109 & INLP rank 1 & INLP rank 1 & .2432 \\
\hline
\end{tabular}
\caption{Camelyon17 selections. Every natural external diagnostic is
unestimable because a required source class is absent.}
\label{supp:tab:cam-exact-selections}
\end{table}

Across the 325 paired objectives, transform-exact is no worse on every row and
strictly better on 135, with mean, median, and maximum gains of .01036,
$2.6\times10^{-15}$, and .03451. The effectively zero median reflects exact
ties on the 190 rows for which the fallback is already tight. Candidate
deployments increase from 130 to 131. The only decision-status crossing is
Waterbirds seed 107, which is externally estimable and safe. All five BiasBios
selections remain safe. CivilComments and GaitPDB each abstain on five seeds.
Camelyon17 contributes five model-conditional deployments but no estimable
external diagnostic, exactly matching the missing-source theorem.

The independent audit recomputes every confidence radius, both certificate
families, both selected frontiers, all external diagnostics, and all 650 global
optimization solutions. It reports zero mismatches, pointwise dominance, and
no failures. The manifest digest is
\texttt{c12f18c9b52bb68522691386131faad9}\allowbreak
\texttt{66c1ae60d9cb0c540af8b909dd1eecc8}; the audit digest is
\texttt{becebaa2839c776fcd806d3d8222a1e2}\allowbreak
\texttt{8c213259300a7781a124bf3feb8fd600}.

\paragraph{Preserved predecessor evidence.}
An earlier lock on seeds 100--104 evaluated only the capacity fallback: five
BiasBios selections were estimable and safe, five Camelyon17
selections were unestimable, and 15 jobs abstained. After those outcomes were
known, an explicitly exploratory exact replay improved 133 of 325 rows and
added two safe Waterbirds deployments. That result motivated the fresh paired
protocol above; it is not pooled with or substituted for the new confirmation.
The earlier preregistration, manifest, fallback audit, exploratory analysis,
and exploratory audit remain in the anonymous artifact for a complete record.

As throughout the paper, external safety here is descriptive. The zero false
acceptances among six estimable selections has a two-sided 95\% Clopper--Pearson
upper bound of 45.9\%, and a favorable benchmark split cannot establish
membership in the structured shift class.
