\section{Transform-Exact Confirmation and Audit Amendment}

The strict-decision v2 preregistration, 10,000-row report, and independent
audit are linked by the consolidated release manifest.

\paragraph{Declared numerical amendment.}
The original v1 confirmation passed every pre-audit gate, but its independent
replay marked two of 10,000 deployment decisions as mismatches. All 80,000
recomputed certificate and external-risk quantities matched. The two returned
capacity-fallback channels exceeded the source-leakage threshold by
$4.12\times10^{-10}$ and $4.40\times10^{-10}$: below the solver's $10^{-9}$
feasibility and $2\times10^{-7}$ post-hoc tolerances, but above the replay's
$10^{-10}$ decision tolerance. We preserved the failed audit, changed the
deployment layer to recheck every source-leakage certificate at $10^{-10}$, and
recorded before rerunning that exactly those two rows should flip to abstention
without changing any primary gate. The hash-locked v2 rerun matched that
prediction exactly; its audit has zero mismatch.

\begin{table*}[t]
\centering
\small
\setlength{\tabcolsep}{4.2pt}
\begin{tabular}{llrrrrrr}
\hline
Scenario & $n$ & \multicolumn{2}{c}{Safe deploy (\%)} &
\multicolumn{2}{c}{Mean cert. error} & Mean gain (pp) & False \\
&& transfer & exact & transfer & exact && accepts \\
\hline
Hard boundary & 125 & 0.0 & 0.0 & .5004 & .4959 & 0.45 & 0/2000 \\
Retention & 125 & 0.3 & 53.0 & .4808 & .4482 & 3.26 & 0/2000 \\
Retention & 250 & 57.8 & 99.9 & .4479 & .4070 & 4.09 & 0/2000 \\
Retention & 500 & 100 & 100 & .4162 & .3799 & 3.63 & 0/2000 \\
Retention & 1000 & 99.8 & 100 & .3888 & .3612 & 2.77 & 0/2000 \\
\hline
\end{tabular}
\caption{Every locked transform-exact confirmation cell. Each method has 1,000
paired tables per row. The exact objective is no larger on all 5,000 pairs and
strictly smaller on all 4,000 retention pairs.}
\label{supp:tab:exactcells}
\end{table*}

The confidence event holds on 999 of 1,000 tables in the hard cell, on all
retention $n=125$ tables, on 999 tables at $n=250$ and $500$, and on all tables
at $n=1000$. There are no failures on the confidence event and no observed
false acceptances off it. For zero events in 1,000 trials, the exact 95\%
binomial upper endpoint is 0.3682\% per method--cell; this empirical endpoint is
distinct from the theorem's familywise $\delta=0.05$ guarantee.

The exploratory five-threshold receipt reuses the audited channels and exact
population risks, holds the source-leakage threshold at .35, and changes only the
utility decision threshold. Because four thresholds were selected after
outcomes, the sensitivity table in the main paper is explicitly descriptive.
All 20 method--size--threshold cells have zero false acceptance, and exact
retention is never lower than capacity transfer.

\section{Transform-Exact Verification Matrix}

The exact support implementation is checked in three independent ways. At zero
radius, source leakage, and utility match a population evaluator that enumerates every
transform extreme, attacker assignment, and residual simplex vertex. For
binary fine alphabets, confidence-ball endpoint enumeration reproduces the
support-function result. Finally, 100 randomized instances verify that the
exact envelope never exceeds the capacity fallback. The optimizer is
then checked against dense channel grids and an independent post-solve
certificate recomputation. Eleven focused transform-exact tests pass as part of
a repository-wide run of 217 tests plus 14 subtests.
